### 2010-06-11 code/subarchitectures/visualization.sa/trunk/doc/v11n.tex
v11n: docs

The library provides a display server that displays objects created by its
clients.  The objects that are on the display server are grouped into views.
Initially every new object is displayed in its own view that has the same name
as the object.
\todo{(TODO: Additional views that display multiple objects can be defined on the server)}
The display server creates rendering contexts in which the views are displayed.
There are two types of contexts: 2D and OpenGL.
% (TODO: new contexts: tabular; textual; ...)

@@

Currently the following types of objects are supported: images, SVG graphics and
OpenGL objects define with LuaGl script or as TomGine render-models.

>>>>

The library provides a display server that displays objects created by its
clients.  The objects that are on the display server are grouped into views.
Initially every new object is displayed in its own view that has the same name
as the object.
\todo{(TODO: Additional views that display multiple objects can be defined on the server)}
The display server creates rendering contexts in which the views are displayed.
There are three types of contexts: 2D, OpenGL and HTML.
% (TODO: new contexts: tabular; textual; ...)

@@

Currently the following types of objects are supported: images, HTML documents,
SVG graphics and OpenGL objects defined with LuaGl script or as TomGine
render-models.
